An ultra-low noise, high-voltage piezo driver

### 2016-11-06 piezo.tex
Edits responding to referees

Laboratory devices are often operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to stabilize the output of a particular system.
For example, the frequency of an extended-cavity diode laser can be locked by feeding back to a piezo-actuated diffraction grating or mirror, which in turn supplies optical feedback to the diode.
Commercially available piezoelectric drivers typically provide a modulation input for  such closed-loop applications, but  the input voltage is often gained such that it spans the entire output range of the device.
While this has certain advantages, many applications would benefit from an architecture that provides a unity-gain, DC-coupled feedback path to the high-voltage output. 
This low-gain modulation input could make closed-loop systems less susceptible to noise contributions from the servo controller, which we often find in our laboratory to be a limiting factor in laser lock stability.

Instrumentation electronics capable of supplying high voltages traditionally fall under one of two architectural umbrellas: DC-DC switching converters, and linear-type amplifiers.
While DC-DC converters are efficient and can work at very high voltages, they suffer from switching noise and limited control bandwidths.
Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high-voltage linear regulator or more typically from a secondary switching converter.
While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection\cite{PA84Datasheet}, high-voltage op-amps require substantially more power than an equivalent switching circuit and are more cumbersome to deploy in the laboratory.

@@

The design principles discussed below show how we leverage the characteristics of a galvanically-isolated switching regulator without sacrificing the low-noise requirements of many laboratory applications.
Our design targets a \SI{250}{\volt} output, but we discuss straightforward modifications to the schematic that make it possible to tailor the gain and output range to a specific application.
The entire electronics package fits into a compact Eurocard rack module (with the high-voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.

@@

@@

\begin{figure}[t!]
\includegraphics[width=\columnwidth]{MOS}
\caption{MOSFET ``quench'' circuit.
When the mid-ground node $\text{V}_\text{MG}$ (also shown in Fig.~\ref{Fig:PiezoCircuit}) goes below the threshold value set at $\text{V}_\text{TH}$, the op-amp puts the HV MOSFET Q1 into conduction.
When engaged, the quench time constant is given by $\tau \approx R_\text{MOS} \text{C}_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}. Capacitor $\text{C}_\text{out}=\SI{1}{\micro\farad}$ is shown in Fig.~\ref{Fig:PiezoCircuit}.
\label{Fig:MOS}}
\end{figure}

@@

One downside of the flyback regulator presented above is that while the switched transformer can quickly charge the output capacitors, the discharge time $\tau$ is limited to {$\approx~\SI{1}{\second}$} by the RC time constant of the circuit.
To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit, as suggested in the DRV2700 datasheet\cite{DRV2700Datasheet}, to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~\ref{Fig:MOS}).
This circuit works by monitoring the voltage at $\text{V}_\text{MG}$, the mid-ground node controlled by op-amp U2.
If $\text{V}_\text{MG}$ drops below a threshold set by $\text{V}_\text{TH}$, the comparator op-amp in Fig.~\ref{Fig:MOS} changes the gate voltage of the MOSFET to put it into conduction.
The time constant for this configuration is given by $\tau \approx R_\text{MOS}\text{C}_\text{out}$.
For our circuit, this changes $\tau$ to $\approx\SI{1}{\milli\second}$, allowing $\text{C}_\text{out}$ to be quickly discharged.
The threshold is $\text{V}_\text{TH} = \SI{-10.4}{\volt}$, but other values could be chosen depending on the design requirements.

\subsection{Auxiliary design features}
\label{Sec:AuxDesign}

Here, we discuss some additional features of our circuit that are independent of the high-voltage design but are advantageous for many applications.
The onboard microcontroller responsible for setting the DAC control voltage, $\text{V}_\text{ctl}$, also interfaces with frontpanel controls including a switch, LCD, and rotary encoder with an integrated pushbutton.
The encoder/pushbutton provide menu navigation, and the switch toggles between DC and scanning operation.
However, other user interfaces can easily be designed to work with the existing hardware.
Arduino-based code\cite{Arduino} written in \CC defines the entire software interaction, and can be modified depending on the needs of the researcher.

The circuit fits into a standard Eurocard module\footnote{Module size is 3U by 12HP by \SI{160}{\milli\meter}, see IEEE~Std~1101.11 for details.}, and is mounted in a Eurocard rack which supplies power at $\pm\SI{15}{\volt}$.
While not required, the rack provides a backplane with analog lines to communicate with other modules (e.g., to implement a current feed-forward for laser diodes as described below).
We are presently designing a backplane with a secondary microcontroller that can be addressed over TCP/IP.
This vastly expands the conceivable control scenarios. 
For example, in our lab we implement a slow-feedback lock of external-cavity diode lasers to a wavemeter.
Software on the computer attached to the wavemeter computes an error signal and corrective control voltage, which will be passed over our internal network to the piezo driver to correct for frequency drifts in the laser.
Other similar schemes are possible, enabling complete remote control of the laser electronics.

The modulation voltage $\text{V}_\text{mod}$ can be supplied either from a BNC on the frontpanel or from the backplane.
This may be useful, e.g., with servo controllers that reside in the same rack as the other control electronics.
In either case, this voltage is differentially buffered to break ground loops.
An output voltage monitor (sensed at the inverting node of U2 in Fig.~\ref{Fig:PiezoCircuit}, but not shown) is buffered and connected to a BNC on the frontpanel, an analog signal line on the backplane, and to the microcontroller.\footnote{One drawback of this scheme is that the contribution of $\text{V}_\text{mod}$ is not sensed by the monitor. Future versions will instead monitor $\text{V}_\text{out}$ through a resistive divider, allowing the microcontroller to implement an infinite integrator and drive $\text{V}_\text{mod}$ to \SI{0}{\volt} in closed-loop operation. This will be a very useful feature to prevent the servo controller from railing.}
The backplane monitor could be fed to a low-noise current controller (e.g., one based on the design in Erickson, et. al.~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
The high-voltage output can be interlocked with another signal on the backplane, permitting easy integration with existing laboratory interlock schemes if desired.
Further details on the design features discussed in this section, including sample software, can be found on GitHub.\cite{PiezoDesignFiles}

@@

@@

We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node $\text{V}_\text{out}$.
A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, and residual ripple from the DRV2700) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) noise estimates in different frequency bands.
We will neglect noise appearing at node $\text{V}_\text{mod}$ due to the external modulation because its exact character depends on the external drive.

@@

\subfloat{
\centering
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} llcc}
\hline\hline
\rule{0pt}{2.5ex}\multirow{2}{*}{Noise source} & & RMS Voltage & RMS Voltage \\
& & (\SI{1}{\hertz}~--~\SI{10}{\hertz})\rule[-1ex]{0pt}{1ex} & (\SI{10}{\hertz}~--~\SI{100}{\kilo\hertz})\rule[-1ex]{0pt}{1ex} \\
\hline
\rule{0pt}{2ex}op-amp voltage & ($e_{v,\text{U2}}$)  & \SI{26}{\micro\volt} & \SI{31}{\micro\volt}      \\
op-amp voltage &  ($e_{i,\text{U2}}$)  &            \SI{51}{\micro\volt}     & \SI{73}{\micro\volt}      \\
DAC             &  ($e_{n,\text{DAC}}$)  &          \SI{28}{\micro\volt}    & \SI{8}{\micro\volt}       \\
Johnson-Nyquist &   ($e_{n,\text{JN}}$)  &         \SI{3}{\micro\volt}    & \SI{14}{\micro\volt}        \\ 
DRV2700 & ($e_{n,\text{DRV}}$) &        \SI{15}{\micro\volt}   & \SI{43}{\micro\volt} \\
\hline
\rule{0pt}{2ex}\textbf{total (calculated)} & & \SI{66}{\micro\volt} & \SI{92}{\micro\volt}  \\
\hline\hline
\end{tabular*}
}
\caption{Noise contributions (color online). Plotted are the noise contributions from each source in our model, along with the total calculated noise. Power spectral density (PSD) is referred to the high-voltage output, and the table shows the integrated RMS noise due to each noise source in different frequency bands. The total RMS noise (summed in quadrature) over the entire \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} range is calculated to be \SI{113}{\micro\volt}, with the residual DRV2700 switching noise measured at \SI{100}{\volt} as described in the text. Frequency-dependent noise spectra for the DAC and op-amp were extracted from the datasheets.\label{Fig:NoisePlot}}
\end{figure}

We now calculate gains from the inverting node of U2.
Because any currents appearing at this node will be cancelled by the feedback of U2, the transimpedance gain $G_{-}^{(i)}$ is simply the impedance $Z_1$, given by
\begin{align}
G_{-}^{(i)} = Z_1 \equiv \frac{R_1}{1+2\pi \iu f R_1 C_1}\,.
\end{align}
%The voltage gain from this node is similarly given by
%\begin{align}
%G_{-}^{(v)} = -Z_1 \left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\,.
%\end{align}
With these expressions in hand, we can calculate the output noise contribution from each source in our model.

\begin{figure}[t]
\includegraphics[width=\columnwidth]{VoltagePSD}
\caption{Voltage noise power spectral density at various output voltages (color online). The integrated RMS noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$, with no output load. The dashed black line indicates the total noise estimate from our model, calculated at \SI{100}{\volt} (see Fig.~\ref{Fig:NoisePlot}).\label{Fig:PSD}}
\end{figure}

Next, we calculate the DAC noise contribution.
The voltage gain from the node $\text{V}_{\text{ctl}}$ is given by
\begin{align}
\label{Eq:Gdc}
G^{(v)}_{\text{ctl}} &= \left[\frac{1}{1+2\pi \iu f R_\text{LP} C_\text{LP}}\right]G_{+}^{(v)}\,,
\end{align}
where the bracketed term represents the contribution to the transfer function from the switchable low-pass filter.
Without the addition of this low-pass filter, the voltage noise of the DAC would dominate both the low- and high-frequency noise performance of the circuit.
A simple solution would be to place a fixed-corner filter at this node, but this would severely restrict the AC performance of $\text{V}_\text{ctl}$.
Thus, we use a switchable low-pass filter (as described in Sec.~\ref{Sec:SlowModulationMOS}) to achieve low-noise performance during DC operation, while still permitting the DAC to modulate $\text{V}_\text{ctl}$ more quickly when needed.
%In our circuit, the high-corner filter is comprised of a \SI{20.5}{\kilo\ohm} resistor and \SI{47}{\nano\farad} capacitor, with $f_c \approx \SI{165}{\hertz}$.
%In DC mode, a secondary \SI{10}{\micro\farad} capacitor in parallel with the \SI{47}{\nano\farad} capacitor mentioned above can be connected to ground through a low resistance digital switch.
%This changes the corner frequency to \SI{0.8}{\hertz}.
The non-zero resistance of the switch contributes a zero to the transfer function at $\approx\SI{23}{\kilo\hertz}$, but has negligible effect on the performance.
The DAC voltage noise contribution can now be calculated as 
\begin{align}
e^2_{n,\text{DAC}} = \big|G^{(v)}_{\text{ctl}}\big|^2 v^2_{n,\text{DAC}}\,,
\end{align}
where $v_{n,\text{DAC}}$ is the frequency-dependent output voltage noise of the DAC as reported in the datasheet.\cite{AD56XXRDatasheet} 
In subsequent calculations, we take the DC-mode operation ($f_c = \SI{0.8}{\hertz}$) for the switchable low-pass filter.

\begin{figure}[b]
\includegraphics[width=\columnwidth]{TimeDomain}
\caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}, color online). (a) Short-time scatterplot  (AC coupled). 
%Points are colored based on the Gaussian spread in acquired voltages, thus indicating the RMS width of the trace.
%The points have been down-sampled and colored based on their probability of occurence, thus providing a visual estimation of the RMS width.
The points have been down-sampled for clarity, and colored based on a normally-distributed probability of occurence in each 100-\si{\micro\second} timeslice (scaled to the most probable voltage).
The color thus provides a visual estimation of the RMS width.
%At each time bin, the points have been colored based on a normally-distributed probability of occurrence, scaled to the most probable voltage for that bin.
%The points have been binned down-sampled and colored based on their probability of occurence, normalized to the most probable voltage in each time bin, thus providing a visual estimation of the RMS width.
(b) Long-term trace, measured on a Keithly~2010 digital multimeter. A~\SI{100}{\volt} DC offset is subtracted from the plotted values. The top panel shows the lab temperature during the same time period.\label{Fig:TimeDomain}}
\end{figure}

@@

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{PiezoModulationTransfer}
\caption{Modulation input transfer function (color online). The solid blue line indicates the unloaded frequency response, while the dash-dotted orange trace shows the response with a \SI{700}{\nano\farad} piezoelectric actuator~{(Thorlabs PN~AE0505D08F)}. Mechanical resonances above $\approx\SI{50}{\kilo\hertz}$ are clearly visible. The dashed green trace shows the response under a \SI{1}{\micro\farad} purely capacitive load. Loaded response bandwidth is $\approx~\SI{100}{\kilo\hertz}$, while the unloaded bandwidth is $\approx~\SI{1}{\mega\hertz}$.\label{Fig:TransferFunc}}
\end{figure}

@@

>>>>

Laboratory devices are often operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to stabilize the output of a particular system.
For example, the frequency of an extended-cavity diode laser can be locked by feeding back to a piezo-actuated diffraction grating or mirror, which in turn supplies optical feedback to the diode.
Commercially available piezoelectric drivers typically provide a modulation input for such closed-loop applications, but the input voltage is often gained such that it spans the entire output range of the device.
Other designs separate high- and low-voltage control pathways, which can extend the bandwidth to $\approx\si{\mega\hertz}$, but the low-voltage control is AC-coupled to the output.\cite{Fleming2009a}
While these designs have advantages, many applications would benefit from an architecture that provides a unity-gain, DC-coupled feedback path to the high-voltage output.
This low-gain modulation input could make closed-loop systems less susceptible to noise contributions from the servo controller, which we often find in our laboratory to be a limiting factor in laser lock stability.

Instrumentation electronics capable of supplying high voltages traditionally fall under one of two architectural umbrellas: DC-DC switching converters, and linear-type amplifiers.
While DC-DC converters are efficient and can work at very high voltages, they suffer from switching noise and limited control bandwidths.
Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high-voltage linear regulator or more typically from a secondary switching converter.
While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection\cite{PA84Datasheet}, linear regulators must dissipate excess voltages as heat and so may be more cumbersome to deploy in the laboratory.

@@

The design principles discussed below show how we leverage the characteristics of a galvanically-isolated switching regulator without sacrificing the low-noise requirements of many laboratory applications.
Our design targets a \SI{250}{\volt} output, but we discuss straightforward modifications to the schematic that make it possible to tailor the gain and output range to a specific application.
The entire electronics package fits into a compact Eurocard rack module (with the high-voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
The output current will be limited by the switching regulator and by the LM7171 op-amp used for low-noise stabilization (U2 in Fig.~\ref{Fig:PiezoCircuit}, which can supply at most $\approx\SI{100}{\milli\ampere}$\cite{LM7171Datasheet}), but is sufficient for nearly all piezoelectric applications.

@@

%% place figure here for better text flow
\begin{figure}[t!]
\includegraphics[width=\columnwidth]{MOS}
\caption{MOSFET ``quench'' circuit.
When the mid-ground node $\text{V}_\text{MG}$ (also shown in Fig.~\ref{Fig:PiezoCircuit}) goes below the threshold value set at $\text{V}_\text{TH}$, the op-amp puts the HV MOSFET Q1 into conduction.
When engaged, the quench time constant is given by $\tau \approx R_\text{MOS} \text{C}_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}. Capacitor $\text{C}_\text{out}=\SI{1}{\micro\farad}$ is shown in Fig.~\ref{Fig:PiezoCircuit}, and details of this circuit are discussed in Sec.~\ref{Sec:SlowModulationMOS}.
\label{Fig:MOS}}
\end{figure}

@@

@@

One downside of the flyback regulator presented above is that while the switched transformer can quickly charge the output capacitors, the discharge time $\tau$ is limited to {$\approx~\SI{1}{\second}$} by the RC time constant of the circuit.
To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit\footnote{The quench circuit presented here is based on the pulldown FET discussed in the DRV2700 datasheet, with some additional modifications to suit our purposes.} to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~\ref{Fig:MOS}).
This circuit works by monitoring the voltage at $\text{V}_\text{MG}$, the mid-ground node controlled by op-amp U2.
If $\text{V}_\text{MG}$ drops below a threshold set by $\text{V}_\text{TH}$, the comparator op-amp in Fig.~\ref{Fig:MOS} changes the gate voltage of the MOSFET to put it into conduction.
The time constant for this configuration is given by $\tau \approx R_\text{MOS}\text{C}_\text{out}$.
For our circuit, this changes $\tau$ to $\approx\SI{1}{\milli\second}$, allowing $\text{C}_\text{out}$ to be quickly discharged.
The threshold is $\text{V}_\text{TH} = \SI{-10.4}{\volt}$, but other values could be chosen depending on the design requirements.

The high-voltage design presented here has the flexibility to exist as a standalone circuit or be integrated with other electronics, and we have included several auxiliary features to make this more convenient.
For example, the analog modulation input is differentially buffered to break ground loops, and the digital portion can be interfaced with other devices in the lab to expand conceivable control scenarios.
Secondary features include a divided-down output that can be used as a monitor or fed forward to a low-noise laser diode current controller like the one in Erickson, et. al.~\cite{Erickson2008a}
Of course many variations are possible, and we refer the reader to GitHub for more details on our specific implementation.\cite{PiezoDesignFiles}

@@

To better understand the circuit performance and the measured output noise reported in Sec.~\ref{Sec:Results}, we introduce the noise model shown in Fig.~\ref{Fig:NoiseModel}. 
A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, and residual ripple from the DRV2700, all calculated at the node $\text{V}_\text{out}$) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) noise estimates in different frequency bands.
We will neglect noise appearing at node $\text{V}_\text{mod}$ due to the external modulation because its exact character depends on the external drive.

@@

We now calculate gains from the inverting node of U2.
Because any currents appearing at this node will be cancelled by the feedback of U2, the transimpedance gain $G_{-}^{(i)}$ is simply the impedance $Z_1$, given by
\begin{align}
G_{-}^{(i)} = Z_1 \equiv \frac{R_1}{1+2\pi \iu f R_1 C_1}\,.
\end{align}
With these expressions in hand, we can calculate the output noise contribution from each source in our model.

@@

\subfloat{
    \centering
    \begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} llcc}
    \hline\hline
    \rule{0pt}{2.5ex}\multirow{2}{*}{Noise source} & & RMS Voltage & RMS Voltage \\
    & & (\SI{1}{\hertz}~--~\SI{10}{\hertz})\rule[-1ex]{0pt}{1ex} & (\SI{10}{\hertz}~--~\SI{100}{\kilo\hertz})\rule[-1ex]{0pt}{1ex} \\
    \hline
    \rule{0pt}{2ex}op-amp voltage & ($e_{v,\text{U2}}$)  & \SI{26}{\micro\volt} & \SI{31}{\micro\volt}      \\
    op-amp voltage &  ($e_{i,\text{U2}}$)  &            \SI{51}{\micro\volt}     & \SI{73}{\micro\volt}      \\
    DAC             &  ($e_{n,\text{DAC}}$)  &          \SI{28}{\micro\volt}    & \SI{8}{\micro\volt}       \\
    Johnson-Nyquist &   ($e_{n,\text{JN}}$)  &         \SI{3}{\micro\volt}    & \SI{14}{\micro\volt}        \\ 
    DRV2700 & ($e_{n,\text{DRV}}$) &        \SI{15}{\micro\volt}   & \SI{43}{\micro\volt} \\
    \hline
    \rule{0pt}{2ex}\textbf{total (calculated)} & & \SI{66}{\micro\volt} & \SI{92}{\micro\volt}  \\
    \hline\hline
    \end{tabular*}
}
\caption{Modeled noise contributions (color online). Plotted are the noise contributions from each source in our model, along with the total calculated noise. Power spectral density (PSD) is referred to the high-voltage output, and the table shows the integrated RMS noise due to each noise source in different frequency bands. The total RMS noise (summed in quadrature) over the entire \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} range is calculated to be \SI{113}{\micro\volt}, with the residual DRV2700 switching noise measured at \SI{100}{\volt} as described in the text. Frequency-dependent noise spectra for the DAC and op-amp were extracted from the datasheets.\label{Fig:NoisePlot}}
\end{figure}

Next, we calculate the DAC noise contribution.
The voltage gain from the node $\text{V}_{\text{ctl}}$ is given by
\begin{align}
\label{Eq:Gdc}
G^{(v)}_{\text{ctl}} &= \left[\frac{1}{1+2\pi \iu f R_\text{LP} C_\text{LP}}\right]G_{+}^{(v)}\,,
\end{align}
where the bracketed term represents the contribution to the transfer function from the switchable low-pass filter.
Without the addition of this low-pass filter, the voltage noise of the DAC would dominate both the low- and high-frequency noise performance of the circuit.
A simple solution would be to place a fixed-corner filter at this node, but this would severely restrict the AC performance of $\text{V}_\text{ctl}$.
Thus, we use a switchable low-pass filter (as described in Sec.~\ref{Sec:SlowModulationMOS}) to achieve low-noise performance during DC operation, while still permitting the DAC to modulate $\text{V}_\text{ctl}$ more quickly when needed.
The non-zero resistance of the switch contributes a zero to the transfer function at $\approx\SI{23}{\kilo\hertz}$, but has negligible effect on the performance.
The DAC voltage noise contribution can now be calculated as 
\begin{align}
e^2_{n,\text{DAC}} = \big|G^{(v)}_{\text{ctl}}\big|^2 v^2_{n,\text{DAC}}\,,
\end{align}
where $v_{n,\text{DAC}}$ is the frequency-dependent output voltage noise of the DAC as reported in the datasheet.\cite{AD56XXRDatasheet} 
In subsequent calculations, we take the DC-mode operation ($f_c = \SI{0.8}{\hertz}$) for the switchable low-pass filter.

@@

\begin{figure}[b]
\includegraphics[width=\columnwidth]{VoltagePSD}
\caption{Voltage noise power spectral density at various output voltages, as measured on an SR780 spectrum analyzer (color online). The integrated RMS noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$, with no output load. The dashed black line overlays the noise estimate from our model, calculated at \SI{100}{\volt} (see Fig.~\ref{Fig:NoisePlot}).\label{Fig:PSD}}
\end{figure}

@@

\begin{figure}[b]
\includegraphics[width=\columnwidth]{TimeDomain}
\caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}, color online). (a) Short-time scatterplot (AC coupled).
The points have been down-sampled for clarity, and colored based on a normally-distributed probability of occurence in each 100-\si{\micro\second} timeslice (scaled to the most probable voltage).
The color thus provides a visual estimation of the RMS width.
(b) Long-term trace, measured on a Keithly~2010 digital multimeter. A~\SI{100}{\volt} DC offset is subtracted from the plotted values. The top panel shows the lab temperature during the same time period.\label{Fig:TimeDomain}}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{PiezoModulationTransfer}
\caption{Modulation input transfer function (color online). The solid blue line indicates the unloaded frequency response, with the phase plotted in the lower panel. The dash-dotted orange trace shows the response with a \SI{700}{\nano\farad} piezoelectric actuator~{(Thorlabs PN~AE0505D08F)}. Several mechanical resonances above $\approx\SI{50}{\kilo\hertz}$ are clearly visible. The dashed green trace shows the response under a \SI{1}{\micro\farad} capacitive load. Loaded response bandwidth is $\approx~\SI{100}{\kilo\hertz}$, while the unloaded bandwidth is $\approx~\SI{5}{\mega\hertz}$ as indicated by the black dashed lines marking the $\SI{45}{\degree}$ phase margin.\label{Fig:TransferFunc}}
\end{figure}
